Our Galactocentric Reference Frame Is Probably Wrong, and Not by a Little

### 2018-12-05 paper/ms.tex
Update paper

@@

@@

To compute the forces from the frozen potential, we use the simple tree code
\texttt{pykdgrav}\footnote{\url{https://github.com/omgspace/pykdgrav},
commit:\texttt{fbd1ddc}}. We use an opening angle of $0.5$ and exclude stars
at distances $R>50\,\kpc$ in the fiducial reference frame.

We use the initial position and velocity of two star particles in
$\texttt{m12i}$. These two star particles are randomly chosen from all star
particles in the simulation with the following properties:

>>>>

Figure~\ref{fig:one_orbit_wrong_ref} shows that the erroneous observer would
infer significant time evolution in their computed actions. The
95\textsuperscript{th} minus 5\textsuperscript{th} percentiles are $8.7$,
$47.1$, and $19.3\,\actunit$ for $J_r$, $L_z$, and $J_z$, respectively. These
are fractional errors of $26.5\%$, $3.1\%$, and $81.4\%$, respectively.

@@

We now

@@

To compute the forces from the frozen potential, we use the simple tree code
\texttt{pykdgrav}\footnote{\url{https://github.com/omgspace/pykdgrav},
commit: \texttt{fbd1ddc}}. We use an opening angle of $0.5$ and exclude stars
at distances $R>50\,\kpc$ in the fiducial reference frame.

We use the initial position and velocity of two star particles in
$\texttt{m12i}$. These two star particles are randomly chosen from all star
particles in the simulation with the following properties (in the fiducial
reference frame):
\begin{enumerate}
    \item age in the range $(0.25, 0.75)\,\Gyr$,
    \item cylindrical radius in the range $(7.7, 8.7)\,\kpc$,
    \item height (absolute value) less than $0.5\,\kpc$,
    \item $J_r$ and $J_z$ in the range:
        \subitem $(10, 20)\,\actunit$ for the first star,
        \subitem $(40, 60)\,\actunit$ for the second star.
\end{enumerate}
The ids we choose are \texttt{23693026} for the first star and
\texttt{17012804} for the second star. We refrain from calling these ``low''
or ``high'' action stars since the actions are computed in a presumably
incorrect reference frame.

To compute actions, both in the choosing of each of these star particles and
in what follows, we use the package
\texttt{agama}\footnote{\url{https://github.com/GalacticDynamics-Oxford/Agama},
commit: \texttt{0e48336}}. Using only the high-resolution particles, we
compute the symmetrized potential in two components. First, a multipole
expansion with $20$ radial grid points and a max order of $2$ for the
spherical-harmonic expansion is used for the dark matter. Second, a
cylindrical spline expansion with $20$ radial and $z$ grid points, a $0$ order
max index azimuthal-harmonic expansion, $0.2$ and $50\,\kpc$ for the minimum
and maximum radial grid node, $0.02$ and $10\,\kpc$ for the minimum and
maximum $z$ grid node is used for the baryonic matter (stars and gas). In both
cases, axisymmetry is explicitly enforced. Other \texttt{agama} parameters are
left as default.

\subsection{Frame Optimization} \label{ssec:frame_opt}
Figure~\Gus{something} shows the action computed at each time step in the
fiducial reference frame. Clearly there is significant time evolution.
